Carryover effects in free recall reveal how prior experiences influence memories of new experiences

### 2023-01-05 paper/main.tex
working on summaries of demographic data, writing up methods
filled out participants section.   - the paper seems to be turning into something more appropriate for a long-form journal, so i've moved the methods section to after the into

@@

We enrolled a total of 491 Dartmouth undergraduate students across 11
experimental conditions. The conditions included two primary controls (feature
rich, reduced), two secondary controls (reduced (early), reduced (late)), six
order manipulation conditions (category, size, length, first letter, color, and
locaiton), and a final adaptive condition. Each of these conditions are
described in the \textit{Experimental design} subsection below.

Participants were assigned to experimental conditions based loosely on their
date of participation. (This aspect of our procedure helped us to more easily
synchronize the experiment databases across multiple testing computers.)
A complete report... %STOPPED HERE

Our experiment is a variant of the classic free recall paradigm that we term
\textit{feature-rich free recall}. In feature-rich free recall, participants
study 16 lists, each comprised of 16 words that vary along a number of stimulus
dimensions: semantic category, object size, text color, text location, word
length, and starting letter (Fig.~\ref{fig:exp1}). Each list contains four
words from each of four different semantic categories; all other stimulus
features are randomized. After studying each list, the participant attempts to
recall as many words as they can from that list, in any order they choose.
Because each individual word is associated with several well-defined (and
quantifiable) features, and because each list incorporates a diverse mix of
feature values along each dimension, this allows us to evaluate participants'
memory fingerprints in rich detail.

>>>>

% need a summary statement...

We enrolled a total of 491 Dartmouth undergraduate students across 11
experimental conditions. The conditions included two primary controls (feature
rich, reduced), two secondary controls (reduced (early), reduced (late)), six
order manipulation conditions (category, size, length, first letter, color, and
location), and a final adaptive condition. Each of these conditions are
described in the \textit{Experimental design} subsection below.

Participants were assigned to experimental conditions based loosely on their
date of participation. (This aspect of our procedure helped us to more easily
synchronize the experiment databases across multiple testing computers.)  Of the 490 participants
who opted to fill out the demographics survey, reported ages ranged from 17 to 31 years (mean: 19.1; standard deviation: 1.356).
A total of 318 participants reported their gender as female, 170 as male, and 2 participants declined to report their gender.
A total of 442 participants reported their ethnicity as ``not Hispanic or Latino,'' 39 as ``Hispanic or Latino,'' and 9 declined
to report their ethnicity.  Participants reported their races as White (345 participants), Asian (120 participants), Black or African American (31 participants),
American Indian or Alaska Native (11 particiapnts), Native Hawaiian or Other Pacific Islander (4 participants), Mixed race (3 participants), Middle Eastern (1 participant), and
Arab (1 participant).  A total of 5 participants declined to report their race.  We note that several participants reported more than one of racial category.
Participants reported their highest degrees achieved as ``Some college'' (359 participants), ``High school graduate'' (117 participants),
``College graduate'' (7 participants), ``Some high school'' (5 participants), ``Doctorate'' (1 participant), and ``Master's degree'' (1 participant).
A total of 482 participants reported no reading impairments, and 8 reported mild reading impairments such as mild dyslexia.  A total of 489
participants reported having normal color vision and 1 participant reported that they were color blind.  A total of 482 participants
reported taking no prescription medications and having no recent injuries; 4 participants reported having ADHD, 1 reported having dyslexia, 1 reported having
allergies, 1 reported a recently torn ACL/MCL, and 1 reported a concussion from several months prior.  The participants reported consuming 0 -- 3 cups of coffee
prior to the testing session (mean: 0.32 cups; standard deviation: 0.58 cups).  Participants reported their current level of alertness, and we converted
their responses to numerical scores as follows: ``very sluggish'' (-2), ``a little sluggish'' (-1), ``neutral'' (0), ``a little alert'' (1), and ``very alert'' (2).
Across all participants, the full range of alertness levels were reported (range: -2 -- 2; mean: 0.35; standard deviation: 0.89) .

We dropped from our dataset the 1 participant who reported abnormal color vision, as well as 39 participants whose data
were corrupted due to technical failures while running the experiment or during the daily database merges.  In total, this left usable data from
452 participants, broken down by experimental condition as follows: feature rich (67 participants), reduced (61 participants), reduced (late) (41 participants), 
reduced (early), (42 participants), category (30 participants), size (30 participants), length (30 participants), first letter (30 participants),
color (31 participants), location (30 participants), and adaptive (60 participants).  The participant who declined to fill out their demographic
survey participated in the location condition, and we verified verbally that they had normal color vision.

Our experiment is a variant of the classic free recall paradigm that we term
\textit{feature-rich free recall}. In feature-rich free recall, participants
study 16 lists, each comprised of 16 words that vary along a number of stimulus
dimensions: semantic category, object size, text color, text location, word
length, and starting letter (Fig.~\ref{fig:exp}). Each list contains four
words from each of four different semantic categories and two object sizes; all other stimulus
features are randomized. After studying each list, the participant attempts to
recall as many words as they can from that list, in any order they choose.
Because each individual word is associated with several well-defined (and
quantifiable) features, and because each list incorporates a diverse mix of
feature values along each dimension, this allows us to evaluate participants'
memory fingerprints in rich detail.

@@
